Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-10-05 manuscript.Rmd
Cleanup code.

@@

```{r summarySetUp, eval=TRUE}

@@

@@

@@

```{r Figure 1 Small Multiples Paper}
scopus.df < scopus.df %>% filter(Year <= 2013)

@@

ggsave(small_multiples_paper, file = "Figure_1_small_multiples.jpg", dpi = 1200, height = 8, width = 12, units = "in")
```

@@

plotSmallMultiples.2 <- ggplot(sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ],  
     aes(Year, N)) +
     geom_line(colour="#e66101") +
     geom_line(data = sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ], 
     aes(Year, Documents), colour = "#533c99", alpha = .80) + 
     facet_wrap(~ Abbrev) + 
     theme_bw() +
     theme(strip.text.x = element_text(size = 8)) +  
     theme(legend.position = "bottom", 
     panel.grid.minor = element_blank(), 
     axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
     geom_text(data = ldata[41:79, ], aes(x =xpos, y = ypos, label = lab), size =2.5) +
     ylim(c(0,225)) +
     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
     annotate("segment", x = 1989, xend = 1992, y = 215, yend = 215, colour = "#e66101") + 
     annotate("segment", x = 1989, xend = 1992, y = 190, yend = 190, colour = "#533c99") +
     ggtitle("Figure 1 (cont.). Number of Article Records by Journal (1989 - 2013)")
```

```{r Figure 2 Journal Growth, eval = FALSE}
#=======================================
# Journals
#=======================================

@@

(figure2 <- ggplot(n.journals.year, aes(record.y, 
    y = Journal.count)) + 
    theme_bw() + 
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Journals") + 
    scale_y_continuous(breaks = c(seq(0, 100, 10)), limits = c(20, 95)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75)) + 
    geom_line(aes(x = record.y, y = Price, colour = "Estimated 5% CAGR"),
        data = n.journals.year,   colour = cp[2], alpha = .80) +
    geom_line(aes(x = record.y, y = SWHD, colour = "Estimated 4% CAGR"), 
        data = n.journals.year,  colour = cp[2], alpha = .80) +
    geom_line(aes(colour = "Observed Growth"), colour = cp[4], size = 1.5) + 
    stat_smooth(method = "lm", se = FALSE, colour = cp[3]) +
    annotate("text", x = 2016.5, y = 60, label = "3.2% CAGR", size = 5) +
    annotate("text", x = 2016.5, y = 73, label = "Linear growth", size = 5) + 
    annotate("text", x = 2016.5, y = 90, label = "4.7% CAGR", size = 5) + 
    annotate("text", x = 2017.5, y = 65, label = "Observed growth", size = 5) +
    scale_x_continuous(limits = c(1989, 2020), breaks = c(1989, 1993, 1997, 2001, 2005, 2009, 2013)) +
    #ggtitle("Figure 2. Observed Versus Estimated Growth of Journals (1989-2013)") + 
   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
          panel.border = element_blank(), axis.line = element_line(), 
          axis.text.x = element_text(size = 16), 
          axis.text.y = element_text(size = 16), 
          axis.title.x = element_text(size = 16), 
          axis.title.y = element_text(size = 16)) +
    theme(plot.title = element_text(size = 19)))

ggsave(figure2, file = "figure2.jpeg", width = 7, height = 7, units = "in", dpi = 1200)
```

```{r Figure 3 Annual Change, eval=FALSE}
curr <- n.journals.year$Journal.count[-1]
prev <- n.journals.year$Journal.count[1:(length(n.journals.year$Journal.count)-1)]
annualChange.numeric <- c(0, (100 * (curr-prev)/ prev))
annualChange.dichotomous <- ifelse(annualChange.numeric < 0, "Decrease", "Increase")
annualChange.df <- data.frame(annualChange.numeric, annualChange.dichotomous)
annualChange.df$year <- c(1989:2013)

@@

ggsave(figure3, file = "figure3.jpeg", width = 7, height = 7, units = "in", dpi=1200)
```

```{r plot02_SmallMultiples, eval=FALSE}
# Remove 2014 & 2015 
n.so <- filter(full.df, attributes == "journal") %>% mutate(title = record) %>% 
  select(-attributes, -record)

# Read Scopus database
#scopus.df2 <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/scopus_OldHar#vest.csv")

 abb.df$ID <- 1:nrow(abb.df)
 sm.scopus.merged <- full_join(sm.scopus.merged, abb.df, by = "Journal") %>% 
     select(-X) %>%
     mutate(Documents = ifelse(Documents == 0, NA, Documents))

 sm.scopus.merged$Abbrev <- factor(sm.scopus.merged$Abbrev, levels = (title.order))
 sm.scopus.merged <- group_by(sm.scopus.merged, Journal) %>%
     mutate(Overall.Scopus = sum(Documents, na.rm=TRUE)) %>%
     ungroup()
# 
 # Create labels for the facets
 Overall.N <- distinct(sm.scopus.merged, Abbrev) 
 lab1 <- gsub(" ", "", paste("N=", pretty(Overall.N$Overall.N), sep=""))
 lab2 <- gsub(" ", "", paste("N=", pretty(Overall.N$Overall.Scopus), sep=""))
 lab <- paste(lab1, lab2, sep="\n")
 xpos = rep(1999, 80)
 ypos = rep(200, 80)

 Overall.N <- distinct(sm.df, Journal)

 ldata <- data.frame(xpos, ypos, lab, Overall.N$Abbrev) %>% 
     rename(Abbrev = Overall.N.Abbrev)

plotSmallMultiples.2 <- ggplot(sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ],  
     aes(Year, N)) +
     geom_line(colour="#e66101") +
     geom_line(data = sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ], 
     aes(Year, Documents), colour = "#533c99", alpha = .80) + 
     facet_wrap(~ Abbrev) + 
     theme_bw() +
     theme(strip.text.x = element_text(size = 8)) +  
     theme(legend.position = "bottom", 
     panel.grid.minor = element_blank(), 
     axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
     geom_text(data = ldata[41:79, ], aes(x =xpos, y = ypos, label = lab), size =2.5) +
     ylim(c(0,225)) +
     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
     annotate("segment", x = 1989, xend = 1992, y = 215, yend = 215, colour = "#e66101") + 
     annotate("segment", x = 1989, xend = 1992, y = 190, yend = 190, colour = "#533c99") +
     ggtitle("Figure 1 (cont.). Number of Article Records by Journal (1989 - 2013)")
```

```{r Figure 4 CAGR Comparison, eval=FALSE}

CAGR <- function(start, finish, periods){
  # Function to compute the CAGR given simple returns
  #
  # args:
  #  start = starting value
  #  finish = ending cumulative value
  #  periods = number of time periods over which value was accumulated
  #
  # Returns the Compound Annual Growth Rate
    cagr <- round(((finish/start)^(1 /periods) - 1)*100, digits=1)    
  return(cagr)
}

sangam.cumsum <-sangam %>%
  group_by(field) %>%
  mutate(CumSum=cumsum(count))

cagr <- sangam.cumsum %>%
  filter(year==1989 | year==1998)%>%
  group_by(field)%>%
  mutate(cagr=CAGR(start=min(CumSum), finish=max(CumSum), periods=9)) %>%
  select(field, cagr)

cagr<-unique(cagr)

############## Generate comparable social work CAGR, 1989-1998 #################

sw.cagr <- articles.df %>%
  filter(Year<1999 & Year>1988)%>%
  mutate(CumSum=cumsum(N)) %>%
  mutate(field = "socialWork")

sw.cagr <- sw.cagr %>%
  mutate(cagr=CAGR(start=min(CumSum), finish=max(CumSum), periods=9))%>%
  select(field, cagr)

sw.cagr<-unique(sw.cagr)

cagr<-rbind(cagr, sw.cagr)

cagr$field<-as.character(cagr$field)
cagr$field<-reorder(cagr$field, cagr$cagr)

#############PLOT##################

CAGR <- ggplot(cagr, aes(x=field, y=cagr, fill=field, group =1)) + theme_bw() + 
    geom_bar(width=0.8, stat='identity') + theme(axis.text.x = element_text(size=8),
        title = element_text(size = 10), plot.title=element_text(size=10)) + 
    ylab("Compound annual growth rate (%)") + 
    xlab("") + 
    ggtitle("Figure 4. Compound annual growth rates for \nnumber of published articles (1989 - 1998)") + 
    theme(plot.title = element_text(size = rel(1.5))) + scale_y_continuous(breaks =
        c(seq(0, 40,  15)), limits=c(0, 40)) + theme(axis.title.x =
        element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75)) + 
    scale_fill_manual(values=c("#b2abd2", "#b2abd2", "#fdb863", "#b2abd2",
        "#b2abd2", "#b2abd2", "#b2abd2"))+ theme(legend.position="none") + 
    scale_x_discrete(labels=c("Psychology","Economics","Social \nWork","Sociology","Political \nScience", "History", "Anthropology")) + 
    geom_hline(yintercept=seq(0, 40, 15), col="white", lwd=0.6) + 
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),  
        panel.border = element_blank(), axis.line = element_line(), 
        axis.text.y = element_text(size = 15),
        axis.text.x = element_text(size = 15),
        axis.title.y = element_text(size = 15), 
        title = element_text(size = 13)
        ) + 
    geom_text(aes(label =cagr ), vjust = -.5)

>>>>

### Workspace initialization

Set the working directory of this document to the directory containing the historical database.

@@

### Descriptive summaries

```{r Descriptive Summary, eval=TRUE}

@@

### Table 1

@@

print(table1)

@@

### Figure 1 - Small Multiples

This figure is for the manuscript.  Please note that the rendering is optimized for the manuscript, not an online rendering.

```{r Figure 1 Small Multiples Paper}
#scopus.df < scopus.df %>% filter(Year <= 2013)

@@

#------------Create high quality jpeg-----------------

# ggsave(small_multiples_paper, file = "Figure_1_small_multiples.jpg", dpi =  1200, height = 8, width = 12, units = "in")

print(small_multiples_paper)
```

### Small Multiples - Online Supplement

@@

plotSmallMultiples.2 <- ggplot(sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ],  
     aes(Year, N)) +
     geom_line(colour="#e66101") +
     geom_line(data = sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ], 
     aes(Year, Documents), colour = "#533c99", alpha = .80) + 
     facet_wrap(~ Abbrev) + 
     theme_bw() +
     theme(strip.text.x = element_text(size = 8)) +  
     theme(legend.position = "bottom", 
     panel.grid.minor = element_blank(), 
     axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
     geom_text(data = ldata[41:79, ], aes(x =xpos, y = ypos, label = lab), size =2.5) +
     ylim(c(0,225)) +
     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
     annotate("segment", x = 1989, xend = 1992, y = 215, yend = 215, colour = "#e66101") + 
     annotate("segment", x = 1989, xend = 1992, y = 190, yend = 190, colour = "#533c99") +
     ggtitle("Figure 1 (cont.). Number of Article Records by Journal (1989 - 2013)")

print(plotSmallMultiples.1)
print(plotSmallMultiples.2)
```

### Figure 2 - Growth of Social Work Research

```{r Figure 2 Journal Growth, eval = TRUE}
#=======================================
# Journals
#=======================================

@@

figure2 <- ggplot(n.journals.year, aes(record.y, 
    y = Journal.count)) + 
    theme_bw() + 
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Journals") + 
    scale_y_continuous(breaks = c(seq(0, 100, 10)), limits = c(20, 95)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75)) + 
    geom_line(aes(x = record.y, y = Price, colour = "Estimated 5% CAGR"),
        data = n.journals.year,   colour = cp[2], alpha = .80) +
    geom_line(aes(x = record.y, y = SWHD, colour = "Estimated 4% CAGR"), 
        data = n.journals.year,  colour = cp[2], alpha = .80) +
    geom_line(aes(colour = "Observed Growth"), colour = cp[4], size = 1.5) + 
    stat_smooth(method = "lm", se = FALSE, colour = cp[3]) +
    annotate("text", x = 2016.5, y = 60, label = "3.2% CAGR", size = 5) +
    annotate("text", x = 2016.5, y = 73, label = "Linear growth", size = 5) + 
    annotate("text", x = 2016.5, y = 90, label = "4.7% CAGR", size = 5) + 
    annotate("text", x = 2017.5, y = 65, label = "Observed growth", size = 5) +
    scale_x_continuous(limits = c(1989, 2020), breaks = c(1989, 1993, 1997, 2001, 2005, 2009, 2013)) +
    #ggtitle("Figure 2. Observed Versus Estimated Growth of Journals (1989-2013)") + 
   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
          panel.border = element_blank(), axis.line = element_line(), 
          axis.text.x = element_text(size = 16), 
          axis.text.y = element_text(size = 16), 
          axis.title.x = element_text(size = 16), 
          axis.title.y = element_text(size = 16)) +
    theme(plot.title = element_text(size = 19))

#ggsave(figure2, file = "figure2.jpeg", width = 7, height = 7, units = "in", dpi = 1200)

print(figure2)
```

### Figure 3 Annual Change

```{r Figure 3 Annual Change, eval=TRUE}
curr <- n.journals.year$Journal.count[-1]
prev <- n.journals.year$Journal.count[1:(length(n.journals.year$Journal.count)-1)]
annualChange.numeric <- c(0, (100 * (curr-prev)/ prev))
annualChange.dichotomous <- ifelse(annualChange.numeric < 0, "Decrease", "Increase")
annualChange.df <- data.frame(annualChange.numeric, annualChange.dichotomous)
annualChange.df$year <- c(1989:2013)

@@

#ggsave(figure3, file = "figure3.jpeg", width = 7, height = 7, units = "in", dpi=1200)

print(figure3)
```
